Geometron: A Universal Language for Graphical Communication

### 2018-09-11 paper1.tex
writing a paper has updates

Edit style JSON.  Click on the link on the main Geometron

export a png, save it to your computer

svae a svg, link to it, save it to your computer

publish a svg link, share it so others can edit on server and publish edits and share them

Build your own space on quantumart.org/yournamehere email me to set it up.  lafe@quantumart.org

Build your own server, hire me, build a pi locally, build graphics, share and publish on web using a mirror, customize the language, build a physical node for the network in a conference room with a custom keyboard and a projector on a big screen

Customize your code for your brand and your research, publish it all, share your artwork as art

@@

Full workflow:

Read this paper(or skim it and look at the pictures) 
download free graphics for use in your documents from graphics library
try out basic movements, drawing actions, make circles, lines, and gates and circuits
make your own graphics on existing instance shared with you, publish them and use them as needed, learn to read the feeds of other users to also use their graphics productions
create new instance:
replicator.php
navigate to glyph editor, test:
index.php
go to tree, create a new branch on it:
tree.php
go to that branch and start editing it:
index.php?path=mynewpath/
edit the shape table:
shapetableeditor.php?path=mynewpath/
shapes.txt
pastebin.com 
actions, then symbols
index.php?path=mynewpath/
(PUBLISH)
svg/svg[datecode].svg $\rightarrow$ web, adobe creative suite, microsoft office suite, inkscape
(PNG PUBLISH)
save as: filename.png $\rightarrow$ powerpoint, word, latex, web
web links$\rightarrow$ svgfeed.php $\rightarrow$ index.php?path=mynewpath/&url=mynewpath/svg/svg[datecode].svg
share and spread to other users, teaching them how to create an instance, use it, modify it and spread it themselves so that the entire system self replicates and evolves based on user needs.

@@

    Graphical documentation of quantum computing languages, simplifying the construction of programs as well as the sharing of them between various types of researcher or expert.

    Running on a local machine, Connecting with Jupyter notebooks and LaTex

Hire me to set up a local node of Network

human workflow: marketing, senior management, frontend web development, fabrication people, measurement researchers, theorists, investors, program managers, public, students,

file structure:

*.php
bytecode/*.txt
svg/*.txt
javascript/*.txt
css/*.txt
html/*.txt
json/*.txt
php/*.txt

files in workflow:
index.php

shapetableeditor.php
shapes.txt

stylejson.txt
currentjson.txt
tree.php

svg/svg[datecode].txt

@@

Try to imagine learning about quantum two level systems without the Bloch sphere, or basic gates without the graphical representation of control not or quantum electrodynamics without Feynman diagrams.  These graphical tools are some of the most powerful we have at our disposal(including computers and lab equipment even) as quantum information scientists.  Imagine if the bar to build a new graphical language like this were lowered to where a graduate student could easily make a new one on their smart phone while waiting for the bus.  We have no idea just how much computational power will be unleashed by creating a free open graphical network for this kind of information, but the only way to find out is to build it.

>>>>

The next thing to experiment with is editing the style JSON file.  This is acomplished by clicking the link marked ``stylejsoneditor.php''.  This links to an editor of a JSON(JavaScript Object Notation) file which holds the present values of all the layers' colors and linewidths.  Be sure to not change the locations of commas and quotation marks, these are critical for the JSON file to be recognized, but change the value of line0 for instance and you can control the linewidth of the default lines drawn.  This is probably the most commonly used aspect of this feature, being able to change linewidth.

With this basic tour of functionality you are ready to actually get some useful files out of this system.  To do this, first click on the button marked ``EXPORT PNG''.  Then right click on the image and you can save or copy the png of what you made.  Of course, the PNG destroys the vector graphics nature of what you've made, it's just easier to share in more types of software.  To get the file in SVG format, click the button marked ``SAVE SVG''.  Now notice that the text field in the lower right corner of the screen has a bunch of code in it.  That is the contents of the SVG, which you can copy and paste into a text editor and save as filename.svg if you want, but the much simpler way to see your file is to click the link to the svg feed link, where it should be the top image.  Right click to save it.

Once you are comforatble with the basics of Geometron, you should explore the tree.php file which has links to various language instances.  From there the next step is to get your own full instance of the Geometron system in your own directory on quantumart.org so that you can edit the code and try things without worrying about other users.  Then to really deploy the system you want to get a instance set up on your own web server and rebrand and retool the whole system for your specific applications, subjects, brand, and group of people.  You can also build a version of this on a local server behind a firewall for communication just inside your group, which I can help with.

Hire me!

@@

@@

@@

Try to imagine learning about quantum two level systems without the Bloch sphere, or basic quantum logic without the graphical representation of control not or quantum electrodynamics without Feynman diagrams.  These graphical tools are some of the most powerful we have at our disposal(including computers and lab equipment even) as quantum information scientists.  Imagine if the bar to build a new graphical language like this were lowered to where a graduate student could easily make a new one on their smart phone while waiting for the bus.  We have no idea just how much computational power will be unleashed by creating a free open graphical network for this kind of information, but the only way to find out is to build it.
